Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with Uniform Kernels

### 2016-02-28 main_paper.tex
Add 'sharp' to paper title to further narrow its scope
Add brief footnote on 'fuzzy RD' to introduction

\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels}
\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

@@

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators \citep{calonico2015}, or for other local
smoothers. \citep{loader2006} However, in this paper we focus on the baseline
case of sharp RD with a local linear model and uniform kernel. Extensions to
fuzzy RD and nonuniform kernels, which require nontrivial changes to the
underlying bootstrap algorithm, as well as developments to address cross sectional dependence,
 are the subject of ongoing research.

>>>>

\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with Uniform Kernels}

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

@@

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators \citep{calonico2015}, or for other local
smoothers. \citep{loader2006} However, in this paper we focus on the baseline
case of sharp RD with a local linear model and uniform kernel. Extensions to
fuzzy RD designs\footnote{%
  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
  ``sharp'' RD, describes situations where the probability of treatment changes
  discontinuously at a known threshold, but by less than 100\%. Then there are
  treated and untreated subjects above and below the discontinuity but the
  treatment effect remains identified.} %
and nonuniform kernels, which require nontrivial changes to the underlying
bootstrap algorithm, as well as developments to address cross sectional
dependence, are the subject of ongoing research.
